Your Paper Title

### 2025-05-15 Master Thesis/thesis.tex
New

\noindent
\textbf{When does it work?}
\begin{itemize}
    \item Yang - Mills theory and gluon scattering.
    \item Scalar - QED. 
    \item Scalar theory $\lambda \phi^4$.
    \item $\mathcal{N} =4$ super Yang - Mills theory.
    \item Gravity. 
\end{itemize}

@@

\subsection{2\,-\,site model}
For simplicity, in this paper we only focus on the smallest block in this condensed moose theory -- 2-site model, which can be represented by the following diagram 
\begin{figure}[H]
    \centering
    \includegraphics[width=0.3\textwidth]{2-site.png}
    \caption{2-site model}
\end{figure}
\noindent
Here we choose a slightly different model, of which the two gauge group are different.

>>>>

\noindent
\textbf{When does it work?}
\begin{itemize}
    \item Yang - Mills theory and gluon scattering.
    \item Scalar - QED. 
    \item Scalar theory $\lambda \phi^4$.
    \item $\mathcal{N} =4$ super Yang - Mills theory.
    \item Gravity. 
    \item $\cdots\cdots$
\end{itemize}

@@

\section{Scattering ampliyudes in 2\,-\,site model}
For simplicity, in this paper we only focus on the smallest block in this condensed moose theory -- 2-site model, which can be represented by the following diagram 
\begin{figure}[H]
    \centering
    \includegraphics[width=0.3\textwidth]{2-site.png}
    \caption{2-site model}
\end{figure}
\noindent
Here we choose a slightly different model, of which the two gauge group are different. The lagrangiian can be written like 
\begin{equation}
    \mathcal{L}=-\frac{1}{2}\mathrm{Tr}(F_1)^2-\frac{1}{2}\mathrm{Tr}(F_2)^2+\mathrm{Tr}[(D_\mu\Phi)^\dagger(D^\mu\Phi)],
\end{equation}
The amplitudes are classified by their multiplicity:

\vspace{1em}
\begin{table}[ht]
\centering
\renewcommand{\arraystretch}{1.3}
\setlength{\tabcolsep}{6pt}
\begin{tabular}{|c|c|c|c|}
    \hline
    \textbf{3-point} & \textbf{4-point} & \textbf{5-point} & \textbf{6-point} \\
    \hline
    $\bm{V_1\Phi\Phi^\dagger}$ & $\bm{V_1V_1V_1V_1}$ & $\bm{V_1V_1V_1V_1V_1}$ & $\bm{V_1V_1V_1V_1V_1V_1}$ \\
    $\bm{V_2\Phi\Phi^\dagger}$ & $\bm{V_2V_2V_2V_2}$ & $\bm{V_2V_2V_2V_2V_2}$ & $\bm{V_2V_2V_2V_2V_2V_2}$ \\
    $\bm{V_1V_1V_1}$ & $\bm{\Phi^\dagger V_1V_1\Phi}$ & $\bm{\Phi^\dagger V_1V_1V_1\Phi}$ & $\bm{\Phi^\dagger V_1V_1V_1V_1\Phi}$ \\
    $\bm{V_2V_2V_2}$ & $\bm{\Phi V_2V_2\Phi^\dagger}$ & $\bm{\Phi V_2V_2V_2\Phi^\dagger}$ & $\bm{\Phi V_2V_2V_2V_2\Phi^\dagger}$ \\
     & $\bm{\Phi V_2 \Phi^\dagger V_1}$ & $\bm{V_2\Phi^\dagger V_1V_1\Phi}$ & $\bm{V_2V_2\Phi^\dagger V_1V_1\Phi}$ \\
     & $\bm{\Phi\Phi^\dagger\Phi\Phi^\dagger}$ & $\bm{\Phi V_2V_2\Phi^\dagger V_1}$ & $\bm{\Phi V_2V_2\Phi^\dagger V_1V_1}$ \\
     & & \textcolor{red}{$\Phi\Phi^\dagger\Phi\Phi^\dagger V_1$} & $\vdots$ \\
     & & \textcolor{red}{$\Phi\Phi^\dagger\Phi\Phi^\dagger V_2$} & $\vdots$ \\
    \hline
\end{tabular}
\caption{Classification}
\end{table}
\subsection{3-point building block}
We have known that the on-shell 3-point amplitudes can be completely determined by the little group scaling, according to the following formulas
\begin{align*}
    A_3^{h_1h_2h_3} &= c\avg{12}^{h_3-h_1-h_2}\avg{31}^{h_2-h_1-h_3}\avg{23}^{h_1-h_2-h_3}
    \quad & h_1+h_2+h_3 < 0 \\[0.5em]
    A_3^{h_1h_2h_3} &= c' [12]^{h_1+h_2-h_3}[23]^{h_2+h_3-h_1}[31]^{h_3+h_1-h_2}
    \quad & h_1+h_2+h_3 > 0
\end{align*}
Because of the specialty of this kind of 2 site gauge theory, there are no direct interaction between gauge boson and scalar, so there are only two kinds of 3-point amplitudes.
\begin{itemize}
    \item 2 scalar 1 gauge boson
    \begin{equation}
        A[1,2,3^+]=\frac{[23][31]}{[12]},\qquad A[1,2,3^-]=\frac{\mdavg{23}{31}}{\avg{12}}
    \end{equation}
    \item 3 gauge boson
    \begin{equation}
        A[3^+,4^+,5^-]=\frac{[34]^3}{[45][53]},\qquad A[3^-,4^-,5^+]=\frac{\avg{34}^3}{\mdavg{45}{53}}
    \end{equation}
\end{itemize}
If there are no exceptions, 1 and 2 always represent the scalar and antiscalar respectively, other number represent the gauge boson.

\subsection{Gauge boson sector}
In this section, we will show how to build the gauge boson scattering. Because there's no direct interaction between gauge boson 1 and gauge boson 2, so we only need to compute one of them.
And although we have already known the formulas for MHV color-ordered amplitudes for gluon scattering -- Parke-Talyor Formula 
\begin{equation}
    A[\cdots,i^-,\cdots,j^-,\cdots]=\frac{\avg{ij}^4}{\mdavg{12}{23}\cdots\mdavg{n-1,n}{n1}}
\end{equation}
also for the anti-MHV amplitudes
\begin{equation}
    A[\cdots,i^+,\cdots,j^+,\cdots]=\frac{[ij]^4}{[12][34]\cdots[n-1,n][n1]}
\end{equation}
Here, we will give an concrete example to show how to use BCFW to compute the 4-point amplitudes $A[3^+,4^+,5^-,6^-]$

\begin{figure}[H]
    \centering
    \includegraphics{4ptg.pdf}
    \caption{4pt gluon}
\end{figure}
We choose the $[3,4\rangle$ shift, and it has been proved that $[+,+\rangle$ shift is valid
\begin{gather}
    \sket{\hat{3}}=\sket{3}-z\sket{4},\qquad \qquad \aket{\hat{4}}=\aket{4}+z\aket{3} \notag\\
    \aket{\hat{3}}=\aket{3}, \qquad \sket{\hat{4}}=\sket{4}.
\end{gather}
The first diagram can be evaluated 
\begin{equation}
    A_1=\frac{[\hat{3}\hat{I}]^3}{[\hat{I}6][6\hat{3}]}\times\frac{1}{s_{36}}\times\frac{\avg{5\hat{I}}^3}{\mdavg{\hat{I}\hat{4}}{\hat{4}5}}
\end{equation}
The point here is that 
\begin{equation}
    \text{Pole position}:\quad \hat{P}_{34}^2=0=\avg{36}[6\hat{3}]\quad \Rightarrow  \quad [6\hat{3}]=0,
\end{equation}
for the similar reason, we can obtain $[\hat{I}6]=[6\hat{3}]=0$, so we conclude that the left part
\begin{equation}
    \frac{[\hat{3}\hat{I}]^3}{[\hat{I}6][6\hat{3}]}=0
\end{equation}
so the first channel is vanishing.

The second diagram can be similarly evaluated
\begin{align}
    A_2&=\frac{\avg{\hat{I}6}^3}{\mdavg{6\hat{3}}{\hat{3}\hat{I}}}\times\frac{1}{s_{36}}\times\frac{[\hat{I}\hat{4}]^3}{[\hat{4}5][5\hat{I}]}\notag \\
       &=\frac{[34]^3}{[34][45][56][61]}
\end{align}
From this, we can conclude that the color-ordered amplitude equals to
\begin{equation}
    A[3^+,4^+,5^-,6^-]=\frac{[34]^3}{[34][45][56][63]}.
\end{equation}
and it can also be expressed by angle brackets interchangeably
\begin{equation}
    A[3^+,4^+,5^-,6^-]=\frac{\avg{56}^3}{\mdavg{34}{45}\!\mdavg{56}{63}}
\end{equation}
Then, 5-point , 6-point can be recursively computed by using BCFW recursion relation.

\subsection{SQCD like sector}
\subsubsection{4-point case}
First we explain the color decomposition in this sector by 4 point amplitude $\Phi^\dagger V_1V_1\Phi$
    \begin{figure}[htbp]
        \centering
        \begin{minipage}[t]{0.32\textwidth}
            \centering
            \includegraphics[width=\linewidth]{sch.pdf}
            \caption{s channel}
        \end{minipage}
        \hfill
        \begin{minipage}[t]{0.32\textwidth}
            \centering
            \includegraphics[width=\linewidth]{uch.pdf}
            \caption{u channel}
        \end{minipage}
        \hfill
        \begin{minipage}[t]{0.32\textwidth}
            \centering
            \includegraphics[width=\linewidth]{tch.pdf}
            \caption{t channel}
        \end{minipage}
    \end{figure}

    The color factor can be written respectively as following
    \begin{equation*}
        r_s=\mathrm{Tr}[\Phi_2^\dagger T^{a_3}T^{a_4}\Phi_1],\quad r_u=\mathrm{Tr}[\Phi_2^\dagger T^{a_4}T^{a_3}\Phi_1],\quad
        r_t=\mathrm{Tr}[\Phi_2^\dagger [T^{a_3},T^{a_4}]\Phi_1]
    \end{equation*}
    We can easily obtain a similar Jacobbi relation
    \begin{equation}
        r_t=r_s-r_u
    \end{equation}
    Then we can accomplish the color decomposition and define the corressponding color-ordered amplitudes.

    For example, in the 4pt. case, the full amplitude can be decomposed to the following form
        \begin{align}
            \mathcal{A}_4(\Phi^\dagger V_1V_1\Phi)&=A_s r_s+A_u r_u+A_t r_t\notag \\
            &=A_s r_s+A_u r_u+A_t(r_s-r_u)\notag\\
            &=(A_s+A_t)r_s+(A_u-A_t)r_u
        \end{align}
        The two subamplitudes can be defined as color-ordered amplitude with order \textcolor{red}{[1,2,3,4]} and 
        \textcolor{red}{[1,2,4,3]} respectively.
        Of course, for the type $\Phi^\dagger(nV_1)\Phi$ and $\Phi (nV_2) \Phi^\dagger$, we can do the same thing to define the color-ordered amplitudes.

    If there is no special case, we always choose the following BCFW shift
        \begin{gather}
            \sket{\hat{2}}=\sket{2}-z\sket{3},\qquad \qquad \aket{\hat{3}}=\aket{3}+z\aket{3}\notag\\
            \aket{\hat{2}}=\aket{2}, \qquad \sket{\hat{3}}=\sket{3}
        \end{gather}
    where 2 always refers to antiscalar and 3 refers to gauge boson with + helicity.

    We start from the 4-point color-ordered $A[1,2,3^+,4^-]$ again
    \begin{center}
    \begin{minipage}{0.45\textwidth}
        \begin{align*}
        A[1,2,3^+,4^-] &= \sum_{h}
        \end{align*}
        \end{minipage}
        \hspace{-3em}
        \begin{minipage}{0.45\textwidth}
        \raisebox{-1em}{\scalebox{0.8}{\includegraphics{4pt1.pdf}}}
        \end{minipage}
    \end{center}

    $\hspace{13.7em} =\raisebox{-2.5em}{\scalebox{0.7}{\includegraphics{4pt1.1.pdf}}}+\raisebox{-2.5em}{\scalebox{0.7}{\includegraphics{4pt1.2.pdf}}}$

    For the same reason, the contribution from the second diagram is vanishing, so we only need to compute the firt one
    \begin{align}
        A_1&=\frac{\avg{\hat{2}\hat{I}}\avg{\hat{I}1}}{\avg{1\hat{I}}}\times \frac{1}{s_{12}}\times \frac{[\hat{I}\hat{3}]^3}{[\hat{3}4][4\hat{I}]}\notag\\
        &=(-1)\frac{\avg{14}^2\avg{24}^2}{\mdavg{12}{23}\!\mdavg{34}{41}}
    \end{align}
    where we use the fact $\aket{\hat{2}}=\aket{2}$, $\sket{\hat{3}}=\sket{3}$, and the \textcolor{red}{Fierz Identity}
    \begin{equation}
        [ij][kl]+[il][jk]+[ik][lj]=0
    \end{equation}

    Here we can prove a nonus relation $\textcolor{red}{A[1,2,3^+,4^+]=0}$. Because of the vanishing of 3 gluon amplitude $A[+,+,+]$, so we only have one channel
    \begin{figure}[H]
        \centering
        \includegraphics{4pt+.pdf}
        \caption{All plus}
    \end{figure}

    Similarly, beacuse of the on-shell pole, we obtain
    \begin{equation}
        [\hat{2}\hat{I}]=[\hat{I}1]=[1\hat{2}]=0,
    \end{equation}
    so the contribution from the left part
    \begin{equation}
        \frac{[\hat{2}\hat{I}][\hat{I}1]}{[1\hat{2}]}=0,
    \end{equation}
    then we can conclude that
    \begin{equation}
        \textcolor{red}{A[1,2,3^+,4^+]=0}
    \end{equation}

\subsubsection{5-point case}

\noindent
Still, from the 4-point amplitude, we can first obtain 
\begin{equation}
    \textcolor{red}{A[1,2,3^+,4^+,5^+]=0}.
\end{equation}
For the 5-point MHV case, here we only consider the $(+,+,-)$ case. 
\begin{align}
    A[1,2,3^+,4^+,5^+]&=\raisebox{-3em}{\scalebox{0.8}{\includegraphics{5pt1.1.pdf}}}+\raisebox{-3em}{\scalebox{0.8}{\includegraphics{5pt1.2.pdf}}}\notag\\
    &=0+\frac{\avg{2\hat{5}}^2\avg{15}}{\avg{12}\!\mdavg{2\hat{I}}{\hat{I}5}}\times\frac{1}{s_{34}}\times\frac{[\hat{3}4]^3}{[4\hat{I}][\hat{I}3]}
\end{align}
then we use
\begin{equation}
    \cbrak{2\hat{I}}{\hat{I3}}=\cbrak{24}{43},\quad \acbrak{4\hat{I}}{\hat{I}5}=\acbrak{43}{\hat{3}5}
\end{equation}
from the pole position
\begin{gather}
    \hat{P}_{34}^2=0=\cbrak{\hat{3}4}{43}\quad \Rightarrow \quad \avg{\hat{3}4}=0\\
    \avg{34}+z\avg{24}=0\qquad\Rightarrow\quad z=-\frac{\avg{34}}{\avg{24}}
\end{gather}
so
\begin{equation}
    \avg{\hat{3}5}=\frac{\mdavg{32}{54}}{\avg{24}}
\end{equation}
Then the color-ordered amplitude equals to 
\begin{equation}
    A[1,2,3^+,4^+,5^-]=\frac{\avg{15}^2\avg{25}^2}{\mdavg{12}{23}\!\mdavg{34}{45}\!\avg{51}}
\end{equation}
\subsubsection{6 - point case}
Similarly, we can obtain all - plus(minus) amplitude equals to 0
\begin{equation}
    A_6[1,2,3^+,4^+,5^+,6^+]=A_6[1,2,3^-,4^-,5^-,6^-]=0.
\end{equation}

For the 6-point MHV amplitude $A_6[1,2,3^+,4^+,5^+,6^-]$, here are the corresponding diagrams
\begin{figure}[H]
    \centering
    \includegraphics[]{6pt1.pdf}
    \caption{6-point MHV}
\end{figure}
For the second diagram of Figure 12, there are pure gauge boson subamplitude $A_4[3^+,4^+,5^+,6^-]=0$, so we conclude the second diagram gives vanishing contribution. For the third diagram, 
\begin{equation}
    \hat{P}_{12}^2=0=2p_1\cdot\hat{p}_2=\cbrak{1\hat{2}}{\hat{2}1}=\cbrak{12}{\hat{2}1}=0 \qquad \Rightarrow \qquad [\hat{2}1]=0
\end{equation}
and similarly
\begin{equation}
    [\hat{2}\hat{I}]=[1\hat{I}]=0.
\end{equation}
The third diagram equals to
\begin{equation}
    A=\frac{[\hat{2}\hat{I}][\hat{I}]1}{[1\hat{2}]}\times\frac{1}{s_{12}}\times A_5[\hat{3}^+,4^+,5^+,6^-,\hat{I}^-]=0.
\end{equation}
The only non-vanishing comes from the first diagram equaling to
\begin{align}
    A&=\frac{\avg{\hat{2}6}^2\avg{61}^2}{\mdavg{1\hat{2}}{\hat{2}\hat{I}}\mdavg{\hat{I}5}{56}\avg{61}}\times\frac{1}{s_{34}}\times\frac{[\hat{3}4]^3}{[4\hat{I}][\hat{I}3]}\notag\\
    &=\frac{\avg{26}^2\avg{61}}{\mdavg{12}{2\hat{I}}\!\mdavg{\hat{I}5}{56}}\times\frac{1}{s_{34}}\times \frac{[34]^3}{[4\hat{I}][\hat{I}]3}
\end{align}
and we have the following equalities
\begin{equation}
    \cbrak{2\hat{I}}{\hat{I}3}+\cbrak{24}{43},\qquad \acbrak{4\hat{I}}{\hat{I}5}=\acbrak{43}{\hat{3}5}
\end{equation}
$\avg{\hat{3}5}$ can be obtained from the on-shell propagator
\begin{equation}
    \hat{P}_{34}^2=0=\cbrak{\hat{3}4}{4\hat{3}}=\cbrak{\hat{3}4}{43}\qquad \Rightarrow\qquad \avg{\hat{3}4}=0,
\end{equation}
then it can be derived that
\begin{equation}
    \avg{\hat{3}5}=\frac{\mdavg{23}{45}}{\avg{24}}.
\end{equation}
Finally, we can conclude that
\begin{align}
    A_6[1,2,3^+,4^+,5^+,6^-]&=\frac{\avg{26}^2\avg{61}\cancel{[34]^3}\cancel{\avg{24}}}{\mdavg{12}{56}\cancel{\avg{24}}\cancel{[43]}\cancel{[43]}\mdavg{23}{45}\cancel{[34]}\avg{43}}\notag\\
    &=(-1)\frac{\avg{26}^2\avg{61}^2}{\mdavg{12}{23}\!\mdavg{34}{45}\!\mdavg{56}{61}}.
\end{align}

Here, we need to notice that in 6-point case, we will first meet the NMHV amplitudes like $A_6[1,2,3^+,4^+,5^-,6^-]$. Although we can still compute it by samely utlizing BCFW recursion relaiton, but it is quite messy. 
\subsubsection{n-point case}
It is not so hard to generallize these results to general case, here we only provide the compact formula, and the negligible sign are neglected
\begin{equation*}
    A[1,2,\cdots,n^-]=\frac{\avg{1n}^2\avg{2n}^2}{\mdavg{12}{23}\cdots\mdavg{n-1,1}{n,1}}
\end{equation*} 
\subsection{Pure 2-site sector}
\subsubsection{4-point case}
The color structure for this kind of amplitude has special form, like
\begin{equation}
    (T_1^{a_1}T_1^{a_2}\cdots T_1^{a_{n_1}})_{ij}(T_2^{b_1}T_2^{b_2}\cdots T_2^{b_{n_2}})_{\bar{j}\bar{i}}
\end{equation}
Here we start from the 4-point case with the color factor
\begin{equation}
    (T_1^a)_{ij}(T_2^b)_{\bar{j}\bar{i}}
\end{equation}
It is more straightforward to observe the color structure in terms of double line notation as follows 
\vspace{0.5em}

\tikzset{every picture/.style={line width=0.75pt}} %set default line width to 0.75pt        
\begin{center}
\begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1,xscale=1]
%uncomment if require: \path (0,300); %set diagram left start at 0, and has height of 300

%Straight Lines [id:da7604191870446242] 
\draw [color={rgb, 255:red, 255; green, 0; blue, 0 }  ,draw opacity=1 ]   (100,100) -- (150,100) ;
%Straight Lines [id:da7895005569652712] 
\draw [color={rgb, 255:red, 0; green, 110; blue, 237 }  ,draw opacity=1 ]   (100,110) -- (190,110) ;
%Straight Lines [id:da19217218880843812] 
\draw [color={rgb, 255:red, 255; green, 0; blue, 0 }  ,draw opacity=1 ]   (150,50) -- (150,100) ;
%Straight Lines [id:da7866299736623521] 
\draw [color={rgb, 255:red, 255; green, 0; blue, 0 }  ,draw opacity=1 ]   (160,50) -- (160,100) ;
%Straight Lines [id:da5667542352395977] 
\draw [color={rgb, 255:red, 0; green, 118; blue, 255 }  ,draw opacity=1 ]   (190,110) -- (190,160) ;
%Straight Lines [id:da33701635654582174] 
\draw [color={rgb, 255:red, 0; green, 118; blue, 255 }  ,draw opacity=1 ]   (200,110) -- (200,160) ;
%Straight Lines [id:da7076492571881566] 
\draw [color={rgb, 255:red, 255; green, 0; blue, 0 }  ,draw opacity=1 ]   (299,100) -- (389,100) ;
%Straight Lines [id:da3803886589182971] 
\draw [color={rgb, 255:red, 0; green, 113; blue, 255 }  ,draw opacity=1 ]   (200,110) -- (250,110) ;
\draw  [color={rgb, 255:red, 255; green, 4; blue, 37 }  ,draw opacity=1 ] (128,103.83) -- (120,100.45) -- (127.97,96.99) ;
\draw  [color={rgb, 255:red, 255; green, 4; blue, 37 }  ,draw opacity=1 ] (153.28,70.33) -- (150.12,78.42) -- (146.44,70.55) ;
\draw  [color={rgb, 255:red, 255; green, 4; blue, 37 }  ,draw opacity=1 ] (156.49,77.35) -- (160.07,69.44) -- (163.33,77.49) ;
\draw  [color={rgb, 255:red, 255; green, 4; blue, 37 }  ,draw opacity=1 ] (340,102.83) -- (332,99.45) -- (339.97,95.99) ;
\draw  [color={rgb, 255:red, 0; green, 119; blue, 255 }  ,draw opacity=1 ] (120.93,107.08) -- (128.98,110.35) -- (121.06,113.93) ;
\draw  [color={rgb, 255:red, 0; green, 119; blue, 255 }  ,draw opacity=1 ] (193.4,129.42) -- (190,137.42) -- (186.55,129.45) ;
\draw  [color={rgb, 255:red, 0; green, 119; blue, 255 }  ,draw opacity=1 ] (196.55,138.41) -- (200,130.44) -- (203.4,138.44) ;
\draw  [color={rgb, 255:red, 0; green, 119; blue, 255 }  ,draw opacity=1 ] (220.93,107.08) -- (228.98,110.35) -- (221.06,113.93) ;
%Straight Lines [id:da696489944746132] 
\draw [color={rgb, 255:red, 0; green, 113; blue, 255 }  ,draw opacity=1 ]   (300,110) -- (350,110) ;
\draw  [color={rgb, 255:red, 0; green, 119; blue, 255 }  ,draw opacity=1 ] (321,107) -- (329.05,110.27) -- (321.13,113.84) ;
%Straight Lines [id:da24340791537710427] 
\draw [color={rgb, 255:red, 0; green, 118; blue, 255 }  ,draw opacity=1 ]   (350,110) -- (350,160) ;
\draw  [color={rgb, 255:red, 0; green, 119; blue, 255 }  ,draw opacity=1 ] (353.4,129.42) -- (350,137.42) -- (346.55,129.45) ;
%Straight Lines [id:da7298898466192736] 
\draw [color={rgb, 255:red, 0; green, 118; blue, 255 }  ,draw opacity=1 ]   (360,110) -- (360,160) ;
\draw  [color={rgb, 255:red, 0; green, 119; blue, 255 }  ,draw opacity=1 ] (356.55,138.41) -- (360,130.44) -- (363.4,138.44) ;
%Straight Lines [id:da3460055698725] 
\draw [color={rgb, 255:red, 0; green, 110; blue, 237 }  ,draw opacity=1 ]   (360,110) -- (450,110) ;
\draw  [color={rgb, 255:red, 0; green, 119; blue, 255 }  ,draw opacity=1 ] (380.93,107.08) -- (388.98,110.35) -- (381.06,113.93) ;
%Straight Lines [id:da4507056480848969] 
\draw [color={rgb, 255:red, 255; green, 0; blue, 0 }  ,draw opacity=1 ]   (389,50) -- (389,100) ;
\draw  [color={rgb, 255:red, 255; green, 4; blue, 37 }  ,draw opacity=1 ] (393.28,70.33) -- (390.12,78.42) -- (386.44,70.55) ;
%Straight Lines [id:da6544383915955476] 
\draw [color={rgb, 255:red, 255; green, 0; blue, 0 }  ,draw opacity=1 ]   (399,50) -- (399,100) ;
\draw  [color={rgb, 255:red, 255; green, 4; blue, 37 }  ,draw opacity=1 ] (395.49,77.35) -- (399.07,69.44) -- (402.33,77.49) ;
%Straight Lines [id:da03624471669725382] 
\draw [color={rgb, 255:red, 255; green, 0; blue, 0 }  ,draw opacity=1 ]   (399,100) -- (449,100) ;
\draw  [color={rgb, 255:red, 255; green, 4; blue, 37 }  ,draw opacity=1 ] (427,103.83) -- (419,100.45) -- (426.97,96.99) ;
%Straight Lines [id:da34280653261510274] 
\draw [color={rgb, 255:red, 255; green, 0; blue, 0 }  ,draw opacity=1 ]   (160,100) -- (250,100) ;
\draw  [color={rgb, 255:red, 255; green, 4; blue, 37 }  ,draw opacity=1 ] (201,102.83) -- (193,99.45) -- (200.97,95.99) ;

% Text Node
\draw (255,97) node [anchor=north west][inner sep=0.75pt]   [align=left] {1};
% Text Node
\draw (81,97) node [anchor=north west][inner sep=0.75pt]   [align=left] {2};
% Text Node
\draw (165,46.4) node [anchor=north west][inner sep=0.75pt]    {$V_{1}$};
% Text Node
\draw (325,143.4) node [anchor=north west][inner sep=0.75pt]    {$V_{2}$};
% Text Node
\draw (407,47.4) node [anchor=north west][inner sep=0.75pt]    {$V_{1}$};
% Text Node
\draw (285,97) node [anchor=north west][inner sep=0.75pt]   [align=left] {2};
% Text Node
\draw (454,95) node [anchor=north west][inner sep=0.75pt]   [align=left] {1};
% Text Node
\draw (166,142.4) node [anchor=north west][inner sep=0.75pt]    {$V_{2}$};

\end{tikzpicture}
\end{center}
For the 4-point case $\mathcal{A}(V_2\Phi^\dagger V_1 \Phi )$, we can construct the color-ordered amplitude from the residue. First, we consider the $(+,-)$ helicity
configuration. There are two feynman diagrams contributing to the color-ordered amplitude.\\
\begin{figure}[htbp]
    \centering
    \includegraphics{4pt.eps}
    \caption{4pt.}
    \label{1}
\end{figure}

Because we choose $[2,3\rangle$ shift here, so there is only one valid BCFW channel
\begin{align*}
    A[1,2,3_1^+,4_2^-]&=\frac{\mdavg{\hat{2}4}{4\hat{I}}}{\avg{\hat{I}\hat{2}}}\times\frac{1}{s_{24}}\times\frac{[\hat{I}\hat{3}][\hat{3}1]}{[1\hat{I}]}\\
    &=\frac{[13][23]}{[14][24]}
\end{align*}
it seems that this amplitude is different from others before, because it is expressed solely in terms of angle brackets, but of course it can be rewritten to another form.
\begin{align*}
    \frac{[13][23]}{[14][24]}&=\frac{\cbrak{23}{31}}{\cbrak{23}{41}}\times \frac{\acbrak{23}{31}}{\acbrak{24}{31}}\\
    &=-\frac{\cbrak{24}{\bcancel{41}}}{\avg{23}\bcancel{[41]}}\times(-1)\frac{\bcancel{[24]}\avg{41}}{\bcancel{[24]}\avg{31}}\\
    &=\frac{\mdavg{14}{24}}{\mdavg{13}{23}}
\end{align*}
Also, we can compute it from direct gluing. For the first diagram, the residue equals to
\begin{equation*}
    \mathrm{Res}|_{s_{12}=0}=\frac{[3 I ] [23]}{[I2]}\times \frac{\avg{I4}\avg{41}}{\avg{1I}}=\frac{\avg{24}[31]\avg{41}[23]}{[42]\avg{24}}
\end{equation*}
Similarly, the second one is
\begin{equation*}
    \mathrm{Res}|_{s_{13}=0}=\frac{\avg{4I}\avg{24}}{\avg{I2}}\times \frac{[31] [I3]}{[1I]}=\frac{\avg{24}[31]\avg{41}[23]}{\avg{32}[23]}
\end{equation*}

Then we can conclude that the four-point color-ordered amplitude $A[1,2,3^+,4^-]$ equals to
\begin{equation*}
    A[1,2,3^+,4^-]=\frac{\avg{24}[31]\avg{41}[23]}{\avg{32}[23][42]\avg{24}}=\frac{\avg{24}\avg{14}}{\avg{13}\avg{23}}
\end{equation*}

\textcolor{red}{$\star Bonus$}

It is still necessary to prove the color-ordered amplitude $A[1,2,3^+,4^+]$ equals to 0. Here we can use the color ordered Feynman rules to show the result.
\begin{equation*}
    A[1,2,3^+,4^+]\propto \frac{\left(\epsilon_3\cdot p_2\right)\left(\epsilon_4\cdot p_1\right)}{s_{23}}+\frac{\left(\epsilon_4\cdot p_2\right)\left(\epsilon_3\cdot p_1\right)}{s_{24}} 
\end{equation*}
Here we can utilize the spinor-helicity variable to express polarization vector
\begin{equation*}
    \epsilon_2^{+\mu}=\frac{\langle r_1 | \gamma^\mu | 3 ]}{\sqrt{2}\avg{r_13}},\qquad \epsilon_4^{+\mu}=\frac{\left <r_2|\gamma^\mu|4\right ]}{\sqrt{2}\avg{r_24}}
\end{equation*}
here $r_1$ and $r_2$ represent the reference spinor.

We can freely choose $r_1=r_2=1$ or 2, then $\avg{r_1 2}$,$\avg{r_2 1}$,$\avg{r_1 1}$,$\avg{r_2 2}$, two of them equal to 0, so we can conclude that
\begin{equation*}
    A[1,2,3^+,4^+]=0
\end{equation*}
\subsubsection{5-point case}
For the 5-point case, we can utilize the BCFW recursion relation which can help us generate higher point amplitude from lower point on-shell subamplitudes. Here, 
we always consider the MHV (Maximal helicity violation) amplitude.

Let us begin with the simplest case $A[1,2,3_1^+,4_1^+,5_2^-]$, where the subscript represent which gauge group the particle belongs to. Because of the property 
of this kind of gauge theory, the color structure is invariant under the OPP (Order Preserving Permutation), in this case, for example,
\begin{equation}
    (3_1^+,4_1^+,5_2^-)\qquad (3_1^+,5_2^-,4_1^+)\qquad(5_2^-,3_1^+,4_1^+)
\end{equation}
give us the same color factor. So in the process of BCFW recursion, these three order offer the same amplitude. We can draw all diagrams contributing to the BCFW process, the first two are following
\par
\begin{figure}[H]
    \centering
    \includegraphics{5pt1.eps}
    \caption{5pt. 1}
    \label{2}
\end{figure}
It is obvious that the second diagram in Figure 13 equals to 0, because there are no interaction between the two gauge bosons.
Similarly, another two diagrams equal to 0 for the same reason
\begin{figure}[H]
    \centering
    \includegraphics{5pt2.eps}
    \caption{5pt. 2}
    \label{3}
\end{figure}
\par
The last diagram still gives 0 contribution because it includes a subamplitude $A[1,\hat{I},\hat{3}^+,4^+]=0$.
\par
\begin{figure}[H]
    \centering
    \includegraphics{5pt3.eps}
    \caption{5pt. 3}
    \label{4}
\end{figure}
Above all. only the first diagram in Figure 1 has non-vanishing contributions, so the full color ordered amplitude equals to
\begin{align}
    A[1,2,3_1^+,4_1^+,5_2^-]&=A[1,2,\hat{I}^+,5^-]\times\frac{1}{s_{34}}\times A[\hat{3}^+,4^+,\hat{I}^-]\notag\\
    &=\frac{\mdavg{15}{25}}{\mdavg{1\hat{I}}{2\hat{I}}}\times\frac{1}{s_{34}}\times\frac{[\hat{3}4]^3}{[4\hat{I}][\hat{I}\hat{3}]}\notag\\
    &=\frac{\mdavg{15}{25}\bcancel{[34]^3}}{\mdavg{14}{23}\avg{43}\bcancel{[43][43][34]}}\\
    &=\frac{\mdavg{15}{25}}{\mdavg{23}{34}\avg{41}}\notag\\
    &=\frac{(-1)\avg{2\textcolor{green}{5}}^2\!\avg{1\textcolor{green}{5}}^2}{\textcolor{blue}{\mdavg{23}{34}\!\avg{41}}\textcolor{red}{\mdavg{25}{51}}}
\end{align}
where we use the fact $|\hat{3}\rangle=|\hat{3}\rangle$ and following identities
\begin{equation}
    \cbrak{1\hat{I}}{\hat{I}3}=\cbrak{14}{43},\quad \cbrak{2\hat{I}}{\hat{I}3}=\cbrak{24}{43}
\end{equation}
and also
\begin{align}
    \frac{[\hat{I}3]}{[4\hat{I}]}&=-\frac{\acbrak{3\hat{I}}{\hat{I}2}}{\acbrak{4\hat{I}}{\hat{I}2}}=-\frac{\acbrak{34}{42}}{\acbrak{43}{\hat{3}2}},\quad(\avg{\hat{3}2}=\avg{32}+z\avg{22}=\avg{32})\notag\\
    &=\frac{\avg{42}}{\avg{32}}
\end{align}
here green refers to the particle with (-) helicity, red refers to particles belong to gauge group 1, red refers to particles belong to gauge group 2.
\par
Similarly, it is very easy to obtain another color-ordered amplitude $A[1,2,3_1^+,4_1^-,5_2^+]$
\begin{align}
    A[1,2,3_1^+,4_1^-,5_2^+]=
    \frac{(-1)\avg{2\textcolor{green}{4}}^2\!\avg{1\textcolor{green}{4}}^2}{\textcolor{blue}{\mdavg{23}{34}\!\avg{41}}\textcolor{red}{\mdavg{25}{51}}}
\end{align}
and also $A[1,2,3_1^-,4_1^+,5_2^+]$ equals to
\begin{equation}
    A[1,2,3_1^-,4_1^+,5_2^+]=
    \frac{(-1)\avg{2\textcolor{green}{3}}^2\!\avg{1\textcolor{green}{3}}^2}{\textcolor{blue}{\mdavg{23}{34}\!\avg{41}}\textcolor{red}{\mdavg{25}{51}}}
\end{equation}
But here we need to emphasize that it is necessary to choose another BCFW shift, like $[1,5^+ \rangle$, as $[2,3^- \rangle$ is not a valid shift. 
\subsubsection{6-point case}
Here we consider $(V_2V_2\Phi^\dagger V_1V_1 \Phi)$ case, the corresponding color-ordered amplitude is $A[1,2,3_1^+,4_1^+,5_2^+,6_2^-]$.
Similarly, the fowwling orders all give us the same color factor
\begin{gather}
    (3_1^+,4_1^+,5_2^+,6_2^-)\qquad(3_1^+,5_2^+,4_1^+,6_2^-)\qquad (3_1^+,5_2^+,6_2^-,4_1^+)\notag\\
